%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%------------------------
% Build as follows
% $ docker build -t latex .
% $ docker run --rm -i -v "$PWD":/data latex pdflatex resume.tex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Agam Kohli} \\ \vspace{1pt}
    \small (734) 945-8291 $|$ \href{mailto:agamkohli9@gmail.com}{\underline{agamkohli9@gmail.com}} $|$ 
    Austin, TX $|$
    \href{https://linkedin.com/in/agam-kohli}{\underline{linkedin.com/in/agam-kohli}} $|$
    \href{https://github.com/agamkohli9}{\underline{github.com/agamkohli9}}
\end{center}


%-----------RELEVANT EXPERIENCE-----------
\section{Relevant Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Oct 2024 -- Present}
      {Arm}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Lead verification enablement for Arm's latest LITTLE core in ARM's big.LITTLE architecture, the energy-efficient processor in mobile SoCs. Coordinate across global design and verification teams.}
        \resumeItem{Deliver monthly releases of Raven, Arm's CPU verification enablement suite used by top-level design verification teams of said core, packaging new ISA-level bug detection capabilities into consistent, stable builds.}
        \resumeItem{Implemented power verification flows in Raven, enabling uni- and multiprocessor systems to verify warm and implementation-defined resets alongside irritators (random interrupts, external debugger events, context changes, etc.), replacing legacy flows and broadening test coverage. }
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Software Engineer}{July 2023 -- Oct 2024}
      {Arm}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Supported CPU verification of architectural and micro-architectural features in ARM Cortex A, R, and M cores.}
        \resumeItem{Developed a register corruption checking feature that intentionally corrupts register values until first legal read/write, enabling detection of unintended register accesses and subtle architectural violations.}
        \resumeItem{Documented and deployed random test generation methodology in C++ and Python.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Founder}{January 2025 -- Present}
      {FortisCard LLC}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Founded an Austin-based startup (\href{https://fortis-card.com}{\underline{fortis-card.com}}) that develops and commercializes a cryptocurrency hardware wallet, FortisCard. Leverages elliptic curve cryptography for transaction signing and hierarchical deterministic key management.}
        % \resumeItem{Managed all aspects of startup development, including product design, technical implementation, market research, and customer outreach.}
        \resumeItem{Implemented all relevant Bitcoin and Ethereum Improvement Protocols in an offline JavaCard running a restricted version of the JVM. This "cold" environment along with an open source stack from firmware to mobile app ensures verifiable end-to-end security for managing cryptocurrency funds.}
      \resumeItemListEnd

	\resumeSubheading
		{CS Research Fellow}{Sept. 2022 -- Dec. 2022}
		{Google}{Remote}
		\resumeItemListStart
			\resumeItem{Selected for Google's competitive 12-week Computer Science Research Mentorship Program 2022B cohort.}
			\resumeItem{Worked 1:1 with a Google mentor on navigating Machine Learning and Compiler research with Apache TVM.}
      \resumeItem{Attended virtual networking events, career panels, tech talks, and information sessions about computing research opportunities.}
		\resumeItemListEnd

	\resumeSubheading
		{AI Fellow}{Aug. 2022 -- April 2023}
		{University of Michigan}{Ann Arbor, MI}
		\resumeItemListStart
			\resumeItem{Fused the basic safety messages from vehicles with bounding boxes from smart intersections in real time to reduce unimpaired crashes by an estimated 90\%.}
			\resumeItem{Validated AI inference data from smart intersection hardware in real time using Gaussian regressions with ground truth data from CAVs (connected and autonomous vehicles) sent through MQTT.}
			\resumeItem{Partnered with AI startup P3Mobility to deploy our product in Ann Arbor intersections.}
			\resumeItem{Attended Entrepreneurship courses with Ann Arbor startups and global treks with high-impact companies in San Francisco to discuss leveraging Entrepreneurship with AI.}
		\resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan}{Aug. 2020 -- April 2023}
      {Bachelor of Science in Engineering, Major in Computer Science}{Ann Arbor, MI}
          \resumeItemListStart
			\resumeItem{3.8/4.0 GPA}
			\resumeItem{Organizations: M-STEM Student Council Board, Michigan Data Science Team,\\Undergraduate Research Opportunity Program}
      \resumeItem{Coursework: Static \& Dynamic Compilers, Computer Architecture, OS, ML, DS/Algorithms, CV, Web Systems}
          \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, ARM Assembly} \\
     \textbf{Softwares}{: LLVM, Lex/Yacc, PyTorch, Apache TVM, Linux} \\
     \textbf{Certifications}{: Scaled Agile Framework (SAFe) 5.0 Practitioner} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

